---
title: "homework"
output: html_notebook
---

# load data/libs
```{r setup}
library(tidyverse)
library(broom)
library(factoextra)

mall <- read_csv("data/mall_customers.csv") %>% janitor::clean_names()
```

# explore data

```{r}
skimr::skim(mall)
```

```{r}
glimpse(mall)
```

```{r}
mall_clean <- mall %>% 
    select(annual_income_k, spending_score_1_100)
mall_clean
```

```{r}
ggplot(mall_clean, aes(x = annual_income_k,
                       y = spending_score_1_100)) +
    geom_point()
```
It appears that there is five possible groups...

- low annual income ~ low spending score
- low annual income ~ high spending score
- median annual income ~ median spending score
- high annual income ~ low spending score
- high annual income ~ high spending score

# find k values

```{r}
fviz_nbclust(mall_clean, 
             kmeans, 
             method = "wss", 
             nstart = 25)
```
This graph is fairly smooth curve - rather than a defined kink.

```{r}
fviz_nbclust(mall_clean, 
             kmeans, 
             method = "silhouette", 
             nstart = 25)
```
Silhouette method is giving k = 5.

```{r}
fviz_nbclust(mall_clean, 
             kmeans, 
             method = "gap_stat", 
             nstart = 25)
```
This gives a result of k = 1.

We get quite different results for each of the methods and for elbow and silhouette many values of k give quite similar results. When there isn’t a clear optimal value of k, and where you don’t have an intuitive value of k before hand, can be a sign data is not well suited for k-means clustering.

#automated process to check k value 1-6
```{r}
#scale values? don't think this changes anything
mall_scale <- mall_clean %>% 
  mutate(across(everything(), scale))
```


```{r}
# function produces a ggplot coloured clusters -> k_val changes the kmeans value...
auto_plots <- function(k_val){
    kmean_fnc <- kmeans(mall_scale, centers = k_val, 
                   nstart = 25)
    
    ret_plot <- augment(kmean_fnc, mall_clean) %>%
        ggplot(aes(annual_income_k, spending_score_1_100, colour = .cluster)) +
        geom_point()+
        ggtitle(paste0("k-means value : ", k_val))
    
    return(ret_plot)
}

for (x in 1:6) {
    i <- auto_plots(x)
    plot(i)
}

rm(x, i)#remove pointer variables for the loop/function combo
```

Based on the graph generated above it appears that a K value of 5, visually looks alright to display the potential groups identified in the initial exploration of the data:

- low annual income ~ low spending score
- low annual income ~ high spending score
- median annual income ~ median spending score
- high annual income ~ low spending score
- high annual income ~ high spending score

Clustering seems to be a good fit for this data set based on the produced graphs above.

```{r}
plot(auto_plots(5))
```

Possible labels for these specific clusters could be for k-value 5:

cluster 1[red]: Careful spenders
cluster 2[olive]: Middle Income
cluster 3[green]: Living beyond means/ Impulse buyers
cluster 4[blue]: Affluent 
cluster 5[pink]: Frugal / Nearing retirement?