---
title: "Homework"
output: html_notebook
---

```{r setup}
library(tidyverse)
library(janitor)
library(infer)
```

# 1.1 MVP
```{r}
animals <- msleep
skimr::skim(animals)
```

```{r}
#check whether animals have 24 hours (sleep_total + awake)
animals %>% 
  mutate(hours = sleep_total + awake) %>% 
  count(hours)
```


# 1.1.2
Jabberwockies sleep for around 7 hours a night, on average

```{r}
#boxplot
animals %>%
  ggplot(aes(x = sleep_total)) +
  geom_boxplot()

#observered sleep_total mean for sampled animals
observed_stat <- animals %>%
  summarise(mean_rating = mean(sleep_total))

observed_stat
```
### Hypothesis test
H0: mean(avg_animals_sleep) & mean(jaberwockies_sleep) == 7
HA: mean(avg_animals_sleep) & mean(jaberwockies_sleep) != 7
alpha: 0.05

```{r}
#null distribution
null_distribution <- animals %>%
  specify(response = sleep_total) %>%
  hypothesize(null = "point", mu = 7) %>%
  generate(reps = 5000, type = "bootstrap") %>%
  calculate(stat = "mean")

#visualise null distro
null_distribution %>%
  visualise(bins = 30) +
  shade_p_value(obs_stat = observed_stat$mean_rating, direction = "both")

#get p value
p_value <- null_distribution %>%
  get_p_value(obs_stat = observed_stat$mean_rating, direction = "both")
p_value
```
### Findings
P-value is close to 0 and less than the significance level of 0.05. 
We therefore reject the NULL hypothesis in favour of the alternative hypothesis. 
There is a difference between average sleep hours of jabberwockies and the animals 
in our sample.


# 1.1.3
```{r}
#check for different food consumption types for the animals (herbivore/carnivore)
animals %>% 
    count(vore)
```
```{r}
animals %>% 
  ggplot(aes(x = sleep_total, y = vore))+
  geom_boxplot()

#get difference in sleep between two dietary types (using infer)
obs_stat_diff <- animals %>% 
  filter(vore == "omni" | vore == "herbi") %>% 
  specify(sleep_total ~ vore) %>% 
  calculate(stat = "diff in means", order = c("omni", "herbi"))
obs_stat_diff
```

Hypothesis
H0: mean(omni_sleep) <= mean(herbi_sleep)
HA: mean(omni_sleep) > mean(herbi_sleep)
alpha: 0.05
```{r}
filtered_animals <- animals %>% 
    filter(vore == "omni" | vore == "herbi")

#null distro
null_distribution <- filtered_animals %>% 
  specify(sleep_total ~ vore) %>% 
  hypothesize(null = "independence") %>% 
  generate(reps = 2000, type = "permute") %>% 
  calculate(stat = "diff in means", order = c("omni", "herbi"))

head(null_distribution)

#visualise distro
null_distribution %>% 
    visualise(bins = 30)+
    shade_p_value(obs_stat = obs_stat_diff$stat, direction = "both")

#get p value
p_value <- null_distribution %>%
  get_p_value(obs_stat = obs_stat_diff$stat, direction = "both")
p_value
```
```{r}
filtered_animals %>% 
    group_by(vore) %>% 
    select(vore, sleep_total) %>% 
    summarise(mean = mean(sleep_total))
```

P-value is 0.244 so we fail to reject to NULL hypothesis. Omnivores do not sleep 
a statistically significantly longer than herbivores.

# 1.1.4

Perform an appropriate statistical test to determine whether the proportion of domesticated animal types in the population of animal types is greater than .

H0: proportion(domesticated) <= 5%.
HA: proportion(domesticated) > 5%
alpha: 0.05

```{r}
domesticated_animals <- animals %>% 
    #alter na values to none
    mutate(conservation = coalesce(conservation, "none")) %>%
    #see if they're domesticated or not
    mutate(is_domestiated = ifelse(conservation == "domesticated", "TRUE", "FALSE"))

#get proportion of domesticated animals
prop_domesticated <- domesticated_animals %>% 
  filter(is_domestiated == "TRUE") %>% 
  summarise(prop = n()/nrow(domesticated_animals))
prop_domesticated
```
```{r}
#null distro
null_dist_domesticated <- domesticated_animals %>% 
  specify(response = is_domestiated, success = "TRUE") %>%
  hypothesise(null = "point", p = 0.05) %>% 
  generate(reps = 2000, type = "draw") %>% 
  calculate(stat = "prop")

#visualise
null_dist_domesticated %>% 
  visualise(bins = 30)+
  shade_p_value(obs_stat = prop_domesticated$prop,
                direction = "greater")


p_val_domesticated <- null_dist_domesticated %>% 
  get_p_value(obs_stat = prop_domesticated$prop,
                direction = "greater")
p_val_domesticated
```
P-value is less than 0.05 so we reject the NULL hypothesis. he amount of
domesticated animals in the population would be statistically greater than 5%.

# 1.2.1

Test: One proportion
H0: prop(know_coffee_shop) <= 40%
HA: prop(know_coffee_shop) > 40%
alpha: 0.05
method_generate_null: draw

# 1.2.2

Test: Two proportion (independant)

`ctr` = `click through rate`
H0: prop(a_ctr) >= prop(b_ctr)
HA: prop(a_ctr) < prop(b_ctr)

method_generate_null: permute

#1.2.3

Test: one mean

H0: mean(part_width) == 145
HA: mean(part_width) != 145

method_generate_null: boostrap


# 1.3.1
`Significance level`: 0.05, `calculated -value`: 0.07

Fail to reject null hypothesis, proportion of people aware of the coffee shop is
less than or equal 40.

# 1.3.2
`Significance level`: 0.01, `-value`: 0.006

Reject null hypothesis in favour of alternative hypothesis, which states group  b 
has more clicks and a group.

# 1.3.3
`Significance level`: 0.05, `-value`: 0.55

Fail to reject the NULL hypothesis. There is no statistically significant difference 
in the size of parts measured the the specification.
