---
title: "Homework"
output: html_notebook
---

```{r setup}
library(tidyverse)
library(janitor)
library(ggfortify)
library(GGally)
library(modelr)
```

# 1
```{r}
houses <- read_csv("data/kc_house_data.csv") %>% clean_names()

names(houses)
skimr::skim(houses)
```

remove unwanted values and add features ready for modelling

yr_renovated - The year of the house’s last renovation
waterfront - A dummy variable for whether the apartment was overlooking the waterfront or not
view - An index from 0 to 4 of how good the view of the property was
condition - An index from 1 to 5 on the condition of the apartment


grade - An index from 1 to 13, where 

    1-3 falls short of building construction and design, 
    7 has an average level of construction and design, and 
    11-13 have a high quality level of construction and design


```{r}
#test grade filter code
houses %>% mutate(grade_test = case_when(
            grade > 10 ~ "high_quality",
            grade >= 8 & grade <= 10 ~ "above_avg",
            grade == 7 ~ "average",
            grade >= 4 & grade <= 6 ~ "below_avg",
            TRUE ~ "low_quality"
        )) %>% 
    select(grade, grade_test)
```


# trim......

```{r}
houses_trim <- houses %>% 
    select(
        #re-order remaining columns
        price,
        everything(),
        #remove misc columns
        -c(id, date, sqft_living15, sqft_lot15, zipcode),
    ) %>% 
    mutate(
        renovated = if_else(yr_renovated == 0, FALSE, TRUE),
        waterfront = as.logical(waterfront),
        grade = case_when(
            grade > 10 ~ "high_quality",
            grade >= 8 & grade <= 10 ~ "above_avg",
            grade == 7 ~ "average",
            grade >= 4 & grade <= 6 ~ "below_avg",
            TRUE ~ "low_quality"
        ),
        view = case_when(
            view == 0 ~ "very_bad",
            view == 1 ~ "bad",
            view == 2 ~ "okay",
            view == 3 ~ "good",
            TRUE ~ "very_good"
        ),
        condition = case_when(
            condition == 1 ~ "very_bad",
            condition == 2 ~ "bad",
            condition == 3 ~ "okay",
            condition == 4 ~ "good",
            TRUE ~ "very_good"
        ),
        price = log(price)
    ) %>% 
    #removed old renovated column
    select(-yr_renovated)


skimr::skim(houses_trim)
```

# 2

```{r}
alias(price ~ ., houses_trim)
```


```{r}
#remove conficting variables
houses_trim <- houses_trim %>% 
  select(-sqft_basement, -sqft_above)
```

```{r}
#doublecheck
alias(price ~ ., houses_trim)
```
# 3

```{r message=FALSE}
houses_tidy_numeric <- houses_trim %>%
  select_if(is.numeric)

houses_tidy_nonnumeric <- houses_trim %>%
  select_if(function(x) !is.numeric(x))

houses_tidy_nonnumeric$price <- houses_trim$price

ggpairs(houses_tidy_numeric, progress =  FALSE)
ggpairs(houses_tidy_nonnumeric, progress = FALSE)
```

Possible candidates for first predictor?

sqft_living - mod1a
sqft_above - mod1b
bathrooms - mod1c
waterfront - mod1d
grade - mod1e


## sqft_living - mod1a
```{r}
mod1a <- lm(price ~ sqft_living,
            houses_trim)
summary(mod1a)
```


```{r}
autoplot(mod1a)
```


## sqft_above - mod1b
```{r}
mod1b <- lm(price ~ sqft_above,
            houses_trim)
summary(mod1b)
```


```{r}
autoplot(mod1b)
```

## bathrooms - mod1c
```{r}
mod1c <- lm(price ~ bathrooms,
            houses_trim)
summary(mod1c)
```


```{r}
autoplot(mod1c)
```

## waterfront - mod1d
```{r}
mod1d <- lm(price ~ waterfront,
            houses_trim)
summary(mod1d)
```


```{r}
autoplot(mod1d)
```


## grade - mod1e
```{r}
mod1e <- lm(price ~ grade,
            houses_trim)
summary(mod1e)
```


```{r}
autoplot(mod1e)
```


sqft_living -> first predictor

```{r}
house_resid <- houses_trim %>% 
  add_residuals(mod1a) %>% 
  select(resid, everything(), -price, -sqft_living)

house_resid %>% 
  ggpairs(aes(colour = grade, alpha = 0.5), progress = FALSE)
```

## Selecting second predictor
```{r}
houses_tidy_numeric <- house_resid %>%
  select_if(is.numeric)

houses_tidy_nonnumeric <- house_resid %>%
  select_if(function(x) !is.numeric(x))

houses_tidy_nonnumeric$price <- house_resid$price

ggpairs(houses_tidy_numeric, progress =  FALSE)
ggpairs(houses_tidy_nonnumeric, progress = FALSE)
```


good options? to test for second predictor

lat - mod2a
waterfront - mod2b
view - mod2c
yr_built - mod2d


## lat - mod2a
```{r}
mod2a <- lm(price ~ sqft_living + lat,
            houses_trim)
summary(mod2a)
```

```{r}
autoplot(mod2a)
```


## waterfront - mod2b
```{r}
mod2b <- lm(price ~ sqft_living + waterfront,
            houses_trim)
summary(mod2b)
```

```{r}
autoplot(mod2b)
```


## view - mod2c
```{r}
mod2c <- lm(price ~ sqft_living + view,
            houses_trim)
summary(mod2c)
```

```{r}
autoplot(mod2c)
```


## yr_built - mod2d
```{r}
mod2d <- lm(price ~ sqft_living + yr_built,
            houses_trim)
summary(mod2d)
```

```{r}
autoplot(mod2d)
```

anova test
```{r}
anova(mod1a, mod2a)
```

Selected lat as second predictor

```{r}
house_resid <- houses_trim %>%
  add_residuals(mod2a) %>%
  select(resid, everything(), -c(lat, price, sqft_living))
```


## Selecting third predictor
```{r}
houses_tidy_numeric <- house_resid %>%
  select_if(is.numeric)

houses_tidy_nonnumeric <- house_resid %>%
  select_if(function(x) !is.numeric(x))

houses_tidy_nonnumeric$price <- house_resid$price

ggpairs(houses_tidy_numeric, progress =  FALSE)
ggpairs(houses_tidy_nonnumeric, progress = FALSE)
```

Possible third predictors
view - mod3a
waterfront - mod3b
yr_built - mod3c

## view - mod3a
```{r}
mod3a <- lm(price ~ sqft_living + lat + view, 
            houses_trim)
summary(mod3a)
```

```{r}
autoplot(mod3a)
```

## waterfront - mod3b
```{r}
mod3b <- lm(price ~ sqft_living + lat + waterfront, 
            houses_trim)
summary(mod3b)
```

```{r}
autoplot(mod3b)
```

## yr_built - mod3c
```{r}
mod3c <- lm(price ~ sqft_living + lat + yr_built, 
            houses_trim)
summary(mod3c)
```

```{r}
autoplot(mod3c)
```

```{r}
anova(mod2a, mod3a)
```

selected view as the third predictor

```{r}
house_resid <- houses_trim %>% 
  add_residuals(mod3a) %>% 
  select(resid, everything(), -c(lat, price, sqft_living, view))
```


4th predictor / interaction?



```{r}
mod4a <- lm(price ~ sqft_living + lat + view + grade, 
            houses_trim)
summary(mod4a)
```
```{r}
autoplot(mod4a)
```

# interation

```{r}
mod5a <- lm(price ~ sqft_living + lat + view + grade + grade:view, 
            houses_trim)
summary(mod5a)
```


```{r}
autoplot(mod5a)
```

