---
title: "HOMEWORK DAY1"
output: html_notebook
---

#import
```{r}
library(tidyverse)
library(CodeClanData)
library(janitor)
```

#datasets
```{r}
revenue_breakdown <- qb_revenue_breakdown %>% clean_names()
monthly_sales <- qb_monthly_sales %>% clean_names()
competitors <- qb_competitors %>% clean_names()
device_data <- qb_device_data %>% clean_names()
```


# MVP 

## 2.1
Q1 
```{r}
ggplot(revenue_breakdown) + 
  aes(x = product, y = revenue, fill = year) + 
  geom_bar(stat = "identity", color = "black") +
  scale_fill_brewer()
```

Q2
```{r}
monthly_sales %>% 
  filter(cashflow == "Kwikbit Unit 1 Sales") %>% 
  ggplot(aes(x = date, y = amount)) +
  geom_line()
```

Q3
```{r}
monthly_sales %>% 
  filter(cashflow != "Kwikbit Unit 1 Sales") %>%
  ggplot() +
  aes(x = date,y = amount, colour = cashflow) +
  geom_line()
```

Q4
```{r}
competitors %>% 
  ggplot() +
  aes(x = year, y = revenue, fill = company) +
  geom_area() +
  scale_y_continuous(labels = scales::dollar)#dollar for revenue
```

Q5
```{r}
competitors %>% 
  ggplot() +
  aes(x = year, y = revenue, colour = company) +
  geom_line() +
  geom_point()
```

Q6

```{r}
device_data %>% 
  mutate(time = hours + (mins/60)) %>% 
  group_by(id, device) %>% 
  mutate(step_count = cumsum(counts)) %>% 
  ggplot() +
  geom_line(aes(x = time, y = step_count, colour = device), show.legend = FALSE) +
  facet_grid(id ~ device) +
  scale_y_continuous(labels = scales::comma) +
  labs(
    title = "\nQikbit 1 vs competitors",
    x = "\nTime",
    y = "Step Count\n"
  ) +
  theme_minimal() +
  theme(plot.title = element_text(size = 16, face = "bold"),
        axis.text = element_text(face="bold"),
  )
  
```

#2.2
q1

col_scheme <- c("#E89FE9", "#50434F", "#B6A7B5", "#F9A472", "#BD7040")

    Adding appropriate labels
    Changing the scales and coordinates when appropriate.
    Applying a unified theme, which is described below:

    Graphs should have white backgrounds, and use colour sparingly.
    There should be faint grid lines.
    Font sizes should be ~12pt although titles should be slightly larger and axis labels can be slightly smaller.
    All plots should use colours from the following company colour scheme.


```{r}
col_scheme <- c("#E89FE9", "#50434F", "#B6A7B5", "#F9A472", "#BD7040")

quickbit_theme <- function(title_text_size = 12, label_text_size = title_text_size - 1)
{
  theme(axis.text= element_text(size = label_text_size,
                                vjust = 0.5),
        plot.title = element_text(size = title_text_size,
                                  hjust = 0.5),
        panel.background = element_rect(fill = "white"),
        panel.grid = element_line(colour = "grey")
        )
}
```


Q1
```{r}
revenue_breakdown %>% 
  ggplot(aes(x = year, y = revenue, fill = product)) +
  geom_col() +
  quickbit_theme()+
  scale_fill_manual(values = col_scheme)
  labs(title = "Revenue from Products Each Year",
       x = "\nYear",
       y = "Revenue (£)\n",
       fill = "Product Type")
```

Q2
```{r}
monthly_sales %>% 
  filter(cashflow == "Kwikbit Unit 1 Sales") %>% 
  ggplot(aes(x = date, y = amount)) +
  geom_line(size = 2, colour = col_scheme[2]) +
  labs(
    title = "Monthly Sales of Kwikbit Unit 1",
    subtitle = "August 2018 to July 2019",
    x = "\nMonth",
    y = "Revenue (£)\n"
  ) +
  quickbit_theme() +
  scale_x_date(date_breaks = "1 month", date_labels =  "%b")
  

```

Q3
```{r}
monthly_sales %>% 
  filter(cashflow != "Kwikbit Unit 1 Sales") %>%
  ggplot(aes(x = date,y = amount, colour = cashflow)) +
  geom_line() +
  labs(title = "Monthly Sales of Kwikbit Unit 1",
       subtitle = "August 2018 to July 2019",
       x = "\nMonth",
       y = "Revenue (£)\n",
       colour = "Cash Flow") +
  quickbit_theme() +
  scale_colour_manual(values = col_scheme) +
  scale_x_date(date_breaks = "1 month", date_labels =  "%b") +
  scale_y_continuous(limits = c(0, 3000))
```

Q4
```{r}
competitors %>% 
  ggplot() +
  aes(x = year, y = revenue, fill = company) +
  geom_area() +
  labs(title = "Annual Sales of Personal Fitness Trackers",
       x = "\nYear",
       y = "Revenue (£Million)\n",
       fill = "Company") +
  quickbit_theme() +
  scale_fill_manual(values = col_scheme) +
  scale_y_continuous(labels = scales::comma)
```

Q5
```{r}
competitors %>% 
  ggplot(aes(x = year, y = revenue, colour = company), legend = "bottom") +
  geom_line() +
  geom_point() +
  quickbit_theme() +
  labs(title = "Annual Sales of Personal Fitness Trackers",
       x = "\nYear",
       y = "Revenue (£Million)\n") +
  theme(legend.position = "bottom") +
  scale_colour_manual(values = col_scheme) +
  scale_y_continuous(labels = scales::comma)
```

Q6
```{r}
device_data %>% 
  mutate(time = hours + mins/60) %>% 
  group_by(id, device) %>% 
  mutate(step_count = cumsum(counts)) %>% 
  ggplot(aes(x = time, y = step_count * 1e-3, colour = device)) +
  geom_line() +
  labs(
    title = "\nQikbit1 vs competitors",
    x = "\nTime",
    y = "Step Count\n",
    colour = "Device"
  ) + 
  quickbit_theme() +
  facet_grid(id ~ device)

```

