---
title: "Homework"
output: html_notebook
---

# MVP

## 1.1
```{r setup}
library(mosaic)
library(mosaicData)
library(janitor)
library(tidyverse)
library(GGally)
library(ggfortify)

housing_prices <- read_csv("data/housing_prices.csv")
```

## 1.2
```{r}
housing_prices %>% select(c('total_rooms', 'total_bedrooms')) %>% 
  ggpairs()
```

Looks like there's a strong positive correlation, and the majority of data clumped together between 1:2000 on y axis

## 1.3
```{r}
housing_prices_alt <- housing_prices %>% select(-total_bedrooms)

# check there are no aliased variables ready for modelling
alias(median_house_value ~ ., data = housing_prices_alt)
```

## 1.4

### 1.4 i
```{r}
ggpairs(housing_prices_alt)
```

### 1.4 ii
```{r}
housing_prices_alt %>% ggplot(aes(x = total_rooms, y = households))+
  geom_point()+
  geom_smooth(method = "lm", se = FALSE)
```


## 1.5
```{r}
housing_prices_alt %>% distinct(ocean_proximity)
```

there are 5 different categories, so we need only four dummy variables (n-1)

## 1.6
```{r}
model <- lm(formula = median_house_value ~ median_income, data = housing_prices_alt)
autoplot(model)
```
plot1: the points are bit too crowded but looks okay
plot2: normal q-q, but is a little bit off 
plot3: acceptable

```{r}
summary(model)
```


## 1.7
```{r}
model_2 <- lm(median_house_value ~ median_income + total_rooms, data = housing_prices_alt)
autoplot(model_2)
```

```{r}
summary(model_2)
```

Residual standard error dropped comparing to the first model that was created.
r squared is slightly higher than the first model and the diagnostics looks very similar to each other.